Variable Selection

### 2015-06-22 var_select.rmd
correct pc.pro by most

```{r, echo=FALSE, include=FALSE}
library('knitr')
# library('knitr', lib = 'C:/Progra~1/R/R-3.1.2/library')
# setwd("C:/Users/n9232371/Documents/Consultbusiness/data")
opts_knit$set(root.dir= "~/OneDrive/shared files/Bligh Tanner/masters/data")
# library('ggplot2', lib = 'C:/Progra~1/R/R-3.1.2/library')
# library("dplyr",lib = 'C:/Progra~1/R/R-3.1.2/library')
# library("plyr",lib = 'C:/Progra~1/R/R-3.1.2/library')
# library('magrittr',lib='C:/Progra~1/R/R-3.1.3/library')
# library('reshape2',lib='C:/Progra~1/R/R-3.1.3/library')
# library("rpart",lib = 'C:/Program Files/R/R-3.2.0/library')
# library('car', lib = 'C:/Progra~1/R/R-3.2.0/library')
# library('e1071', lib = 'C:/Progra~1/R/R-3.2.0/library')
# library('corrgram', lib = 'C:/Progra~1/R/R-3.2.0/library')

library('ggplot2')
library("dplyr")
library("plyr")
library('magrittr')
library('reshape2')
library("rpart")
library('car')
library('e1071')
library('corrgram')
```

@@

>>>>

```{r, echo=FALSE, include=FALSE}

# library('knitr', lib = 'C:/Progra~1/R/R-3.1.2/library')
# library('ggplot2', lib = 'C:/Progra~1/R/R-3.1.2/library')
# library("dplyr",lib = 'C:/Progra~1/R/R-3.1.2/library')
# library("plyr",lib = 'C:/Progra~1/R/R-3.1.2/library')
# library('magrittr',lib='C:/Progra~1/R/R-3.1.3/library')
# library('reshape2',lib='C:/Progra~1/R/R-3.1.3/library')
# library("rpart",lib = 'C:/Program Files/R/R-3.2.0/library')
# library('car', lib = 'C:/Progra~1/R/R-3.2.0/library')
# library('e1071', lib = 'C:/Progra~1/R/R-3.2.0/library')
# library('corrgram', lib = 'C:/Progra~1/R/R-3.2.0/library')
# library('party', lib = 'C:/Progra~1/R/R-3.2.0/library')

library('knitr')
library('ggplot2')
library("dplyr")
library("plyr")
library('magrittr')
library('reshape2')
library("rpart")
library('car')
library('e1071')
library('corrgram')
library('party')

# setwd("~/OneDrive/shared files/Bligh Tanner/masters/data")
opts_knit$set(root.dir= "~/OneDrive/shared files/Bligh Tanner/masters/data")
```

@@

Use cforest from party package - (Strobl etc, 2007)

* must be subsampling without replacement
* subsampling size 0.632 times recommended because about 63.2% of data end up in bootstrap sample
* cforest defauly is unbiased - for unbiased variable importance as per Strobl etc 2007
* since variables are potentially correlated to one another, need to set conditional permutation importance varimp(obj, conditional=TRUE)
    * This iterates each variable against correlated variables in a controlled way. Ie the target variable is assessed against subgroups of the data where a correlated variable is constant.

For cforest, NA values are not handled. Therefore create a 'core' dataframe consisting of the variables which have very low NA entries (say max 10) and delete all NA rows or impute.

State- impute QLD
Business - 22 NA values - impute 'unknown'
Biz.size - 38 NA's - find median, impute?
Biz.type - 18 NA's impute???
charge.ph - delete
charge.pc - delete
Start.Date - delete
End.Date - delete
no.users - 4 NA values - impute
pc.usersss - 7 NA's - what to do. 0 for all? averages for all?
Num.disc - 84 NA's - impute 1?
num.inv and mean.inv- 1 NA?

```{r core_creation}
#impute NA values in some variables to be in core, call this all7b
all7b<- all7a
all7b[is.na(all7b$State),]$State <- 'QLD'
#RSL Care client - now have details
all7b[all7b$code.client %in% 'C2835',]$no.employees <- 1001
all7b[all7b$code.client %in% 'C2835',]$Biz.type <- 'NFP'
all7b[all7b$code.client %in% 'C2835',]$Business <- 'developer/real estate'
all7b[all7b$code.client %in% 'C2758',]$Biz.size <- 'national'
all7b[all7b$code.client %in% 'C2758',]$no.employees <- 2
all7b[all7b$code.client %in% 'C2758',]$Biz.size <- 'local'
all7b[all7b$code.client %in% 'C2758',]$Business <- 'business'
all7b[all7b$code.client %in% 'C2326',]$Business <- 'health'
all7b[all7b$code.client %in% 'C2338',]$Biz.size <- 'local'
all7b[all7b$code.client %in% 'C2338',]$Business <- 'developer/real estate'
all7b[all7b$code.client %in% 'C2338',]$Biz.type <- 'private'
all7b[all7b$code.client %in% 'C2882',]$Biz.size <- 'local'
all7b[all7b$code.client %in% 'C2882',]$Business <- 'builder'
all7b[all7b$code.client %in% 'C2882',]$Biz.type <- 'private'
all7b[all7b$code.client %in% 'C2882',]$no.employees <- 3
#all remaining NA Business will be 'unknown'
all7b$Business<- as.character(all7b$Business)
all7b[is.na(all7b$Business),]$Business <- 'unknown'
all7b$Business<- as.factor(all7b$Business)

#impute Biz.size to be 'local' by default - this is most popular category
all7b[is.na(all7b$Biz.size),]$Biz.size <- 'local'
#impute Biz.type to be 'private' by default - this is most popular category
#client which is 'department of national parks' shall be 'gov'
all7b[is.na(all7b$Biz.type),]$Biz.type <- 'private'
all7b[all7b$code.client %in% 'C2503',]$Biz.type <- 'gov'
#delete charge.ph and charge.pc, Start.Date and End.Date
all7b<- all7b %>% select(-charge.ph, -charge.pc, -Start.Date, -End.Date)
#impute NA no.users as 2 = median and mode
all7b[is.na(all7b$no.users),]$no.users <- 2
#impute NA num.disc as 1 - overwhelmingly the most common
all7b[is.na(all7b$Num.disc),]$Num.disc <- 1
#num.inv and mean.inv both have a single NA value
# this consisted of single large -ve invoice. I think we should delete this case 
all7b<- all7b %>% filter(!is.na(num.inv))
# write.csv(all7b,'all7b.csv')

#create core data frame - variables with very few NA's and delete these NA's

core<- all7b %>% select(code.client , Discipline ,  client.count , inv.mlsto , Business ,
        Biz.size , Biz.type , no.users , Year , timespan , Num.disc , Num.days , mean.peeps,
        pc.contracttech , hours.perday , profit.mlsto , balance.mlsto , hrs.mlsto , 
        cost.mlsto , dis.sc.mlsto , inv.mlsto , return.pdol , code.contact ,
        pc.director , pc.midtech , pc.midpro , pc.gradpro , pc.seniortech , pc.seniorpro ,
        pc.pro , code.director , code.ProjEng , ProjEng.Pos , num.inv , mean.inv , num.neginv , 
        client.meaninv , client.neginv , client.numinv , client.totinv)

var.imp<- cforest(return.pdol~.,
        data= all7b
        )
